How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-03 manuscript/draft_manuscript.Rmd
results outline

>>>>

# Results

## PLOS ONE

* Final sample size
* Breakdown of included articles by year of publication (did/did not include stats section). Final sample broken down by subject classification(s) [most are biology and life sciences]
* Figure showing change in gof measure as function of number of clusters (use to justify choice of number of clusters)

* Desribe topic clusters + examples

## ANZCTR

* Final sample size
